Untrusted B2B Collaboration using the Blockchain

### 2018-07-25 paper/paper.tex
add todos, correct typo
imporve confidence

%TODO correctly show that the address is passed instead of using msg.sender
When a throw event is triggered in the process engine of organization $A$, the process engine of $A$ calls the corresponding \emph{throw event function} on the instance contract of organization $A$.
In the instance contract of $A$ an authorization is performed by looking up the sender address in the access contract of $A$.
If this check is successful, the \emph{catch event function} is called on the partner instance contract of $B$.
In the instance contract of $B$ there is another authorization against the access contract of $A$.
This ensures that both sides can be confident, that the throw event was triggered by an authorized person who belongs to organization $A$.
If this check was also successful, an event is emitted to the blockchain.
This will be detected by the trigger of $B$ and passed to the process engine.
Thus, a message was sent from $A$ to $B$ via the blockchain and an audit trail was created.
An example can be seen in the sequence diagram in Figure \ref{fig:event_sending}.

@@

\subsubsection{Armadillo}

@@

We developed a small command line application for managing users and roles via the access contract.
The application is written in JavaScript in the node.js framework\footnote{\url{https://nodejs.org/}}.
Internally, calls functions on access contracts utilizing the Web3 Ethereum JavaScript API\textsuperscript{\ref{web3}}.
We decide to build the command line functionality with the help of the Vorpal framework\footnote{\url{http://vorpal.js.org/}}.
The README in our repository describes how to use the application.

@@

In the evaluation, we realized that the instantiation cost currently is too high for our system to be used in a productive environment.
Further research thus could be invested into a more decentralized instantiation, where each participant pays for its own instance contract creation.
One approach we discussed, but did not have the time to implement, would be to have the intiator emit a specific instance creation event that each other participant would listen to.
Then, a trigger could be implemented, that calls the \texttt{createInstance} method as soon as the event is received.

>>>>

%TODO correctly show that the address is passed instead of using msg.sender
When a throw event is triggered in the process engine of organization $A$, the process engine of $A$ calls the corresponding \emph{throw event function} on the instance contract of organization $A$.
In the instance contract of $A$ an authorization is performed by looking up the sender address in the access contract of $A$.
If this check is successful, the \emph{catch event function} is called on the partner instance contract of $B$.
In the instance contract of $B$ there is another authorization against the access contract of $A$.
This ensures that both sides can be confident, that the throw event was triggered by an authorized person who belongs to organization $A$.
If this check was also successful, an event is emitted to the blockchain.
This will be detected by the trigger of $B$ and passed to the process engine.
Thus, a message was sent from $A$ to $B$ via the blockchain and an audit trail was created.
An example can be seen in the sequence diagram in Figure \ref{fig:event_sending}.
% TODO explain how payload could look like

@@

% TODO include screenshot
\subsubsection{Armadillo}

@@

We developed a small command line application for managing users and roles via the access contract.
The application is written in JavaScript in the node.js framework\footnote{\url{https://nodejs.org/}}.
Internally, calls functions on access contracts utilizing the Web3 Ethereum JavaScript API\textsuperscript{\ref{web3}}.
We decided to build the command line functionality with the help of the Vorpal framework\footnote{\url{http://vorpal.js.org/}}.
The README in our repository describes how to use the application.

@@

In the evaluation, we realized that the instantiation cost currently is too high for our system to be used in a productive environment.
Further research thus could be invested into a more decentralized instantiation, where each participant pays for its own instance contract creation.
One apporach worth considering is to have the intiator emit a specific instance creation event that each other participant would listen to.
Then, a trigger could be implemented, that calls the \texttt{createInstance} method as soon as the event is received.
